---
title: "Figure A.3"
author: "Stephanie Wilson"
date: "7/14/2020"
output: pdf_document
---

# READ ME  
This code is to create Figure A.2 in the example report in the Sports Nutrition Laboratory Manual. 

## INSTALL PACKAGES  
Only do one-time, then delete this code
```{r}
install.packages(c("ggplot2", "readxl", "RColorBrewer"))
```


## LOAD PACKAGES  
Must do every time a new session is started.
```{r}
library(ggplot2); library(readxl); library(RColorBrewer)
```

## SET WORKING DIRECTORY
The data we need for this plot is on the third spreadsheet of the Excel file titled, "Appendix A Graph Example". Both this RMD and corresponding file must be downloaded and saved in the same folder for the code to operate.  

First, you must set your working directory to the folder where these two files are located. 
```{r}
setwd(file.choose())
```


## LOAD DATA AND DATA SUMMARY FUNCTION
```{r}
#Data
data <- read_excel("Appendix A Graph Example.xlsx", sheet=3)

#Function
data_summary <- function(data, varname, groupnames){
  require(plyr)
  summary_func <- function(x, col){
    c(mean = mean(x[[col]], na.rm=TRUE),
      sd = sd(x[[col]], na.rm=TRUE))
  }
  data_sum<-ddply(data, groupnames, .fun=summary_func,
                  varname)
  data_sum <- rename(data_sum, c("mean" = varname))
 return(data_sum)
}
```

## DO A DATA SUMMARY
This takes your data and calculates mean and standard deviation for your groupings.
```{r}
data2 <- data_summary(data, varname="Power", 
                    groupnames=c("Condition", "Set", "Sprint"))
```

## CREATE YOUR PLOT
You can preview the plot in-line through this RMD file. If you want to export it as an image file or PDF, you can do so by running _PLOT_ in the console tab of the program to generate the image in the plots tab. In the plots tab, there is an export feature where you are able to utilize custom export features.   
```{r}
pd <- position_dodge(0.5)

PLOT <- ggplot(data2, aes(x = Sprint, y = Power, colour = Condition))+
   theme_bw() +
  stat_summary(fun = "mean", geom = "line") +
     geom_point(size = 3, shape = 19, position=position_dodge(width=0.3)) + 
  facet_wrap(~ Set)+
  geom_errorbar(aes(ymin = Power - sd, ymax = Power + sd), width = .1,position=position_dodge(width=0.3)) +
  theme(legend.position = "right")  +
  scale_color_brewer(palette = "Dark2")+ 
  labs(x = "Sprint Number", y="Power Output (Watts)", title="Figure A.3. Average power output for each of the three sprint sets", subtitle = "Bars indicate standard devation.") +
   scale_x_continuous(breaks=seq(1, 6, 1)) +
  scale_y_continuous(limits=c(0,900),breaks=seq(0,900,100)) 

PLOT
```

